\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}
\bibliographystyle{ieeetranN} 
\begin{thebibliography}{22}

\bibitem{} J. Levine, Flex \& bison, 1st ed. Sebastopol, Calif.: O'Reilly Media, 2009.

\bibitem{} C. Donnelly and R. Stallman, CartoCSS, 1st ed. Corto, MA: Free Software Foundation, 1999.

\bibitem{} "User:amisha2016 - OpenStreetMap", openstreetmap.org, 2016. [Online]. Available: https://www.openstreetmap.org/user/amisha2016. [Accessed: 27- Nov- 2017].

\bibitem{} "Customizing OSM Map" , Amisha Budhiraja, 2016. [Online]. Available: https://amisha2016.wordpress.com/2016/11/13/customizing-osm-map/ . [Accessed: 27- Nov- 2017].


\bibitem{} "OpenStreetMap User Manual - Wikibooks, open books for an open world", En.wikibooks.org, 2016. [Online]. Available: http://wiki.openstreetmap.org/wiki/Beginners\_Guide\_1.6. [Accessed: 27- Nov- 2017].

\bibitem{} "User: Amisha Budhiraja pbOSM", GitHub, 2017. [Online]. Available: https://github.com/amisha2016/pbOSM. [Accessed: 27- Nov- 2017].

\bibitem{} "3D OSM Buildings with leaflet", Amisha Budhiraja, 2017. [Online]. Available: https://amisha2016.wordpress.com/2017/07/11/integration-of-3d-osmbuilding-with-leaflet-and-openlayers/. [Accessed: 27- Nov- 2017].

\bibitem{} "openstreetmap", GitHub, 2017. [Online]. Available: https://github.com/openstreetmap. [Accessed: 27- Nov- 2017].
\bibitem{} "Doxygen: Main Page", Doxygen.org, 2016. [Online]. Available: http://www.doxygen.org. [Accessed: 27- Nov- 2017].

\bibitem{} http://www.openstreetmap.org/

\bibitem{} "Increased zoom level to 28 in OSM", Amisha Budhiraja, 2017. [Online]. Available: https://amisha2016.wordpress.com/2017/07/24/inreased-zoom-level-to-28-in-osm/. [Accessed: 27- Nov- 2017].


\bibitem{} "OpenStreetmap - Blogs", openstreetmap.org, 2016. [Online]. Available: https://blogs.openstreetmap.org/. [Accessed: 27- Nov- 2017].

\bibitem{} "JOSM (software)", En.wikipedia.org. [Online]. Available: http://wiki.openstreetmap.org/wiki/JOSM. [Accessed: 27- Nov- 2017].

\bibitem{} "Playing with Languages in OSM", Amisha Budhiraja, 2017. [Online]. Available: https://amisha2016.wordpress.com/2017/07/03/playing-with-languages-in-osm/. [Accessed: 27- Nov- 2017].	

\bibitem{}"Travis CI", En.wikipedia.org, 2017. [Online]. Available: https://en.wikipedia.org/wiki/Travis\_CI. [Accessed: 27- Nov- 2017].

\bibitem{} "CMake/Testing With CTest - KitwarePublic", Cmake.org, 2017. [Online]. Available: https://cmake.org/Wiki/CMake/Testing\_With\_CTest. [Accessed: 27- Nov- 2017].

\end{thebibliography}
