
\section{Future Scope}
OpenStreetMap being an open source project and supported by a large open Source community have a lot of scope for future improvements and additions as other individuals can also contribute in it and add additional functionality. One of the examples is my project only customizer for OpenStreetMap.

Being an Open Source project there is a constant flow of suggestion and demands by people for additional functionality and improvement in existing features.
Customizer being no exception constant flow of feature of suggestions and feature requests even before the start of development. Here is a small list of the Features that would be added in near future.

\begin{enumerate}

\item \textbf{Adding support for Indoor Mapping:} It was decided much at beginning of the project that this feature will be ported using a special syntax then relying on the comment based syntax. The discussion has been going on related to deciding the syntax for the customizer.

\item \textbf{Option to Change Languages:} It has been proposed that there should be a feature to switch to different languages through Javascript.

\item \textbf{Option to import BIM model in JOSM:} This feature will help people especially Civil Engineers to import BIM models in JOSM and customize directly their.

\item \textbf{Styling the map:} There is more need to style a map like adding icy effect near glaciers, show particular tags at particular levels.

\item \textbf{Improving GUI part:} There have been some suggestions related to improving the GUI of the Customizer.
\end{enumerate}

