\section{Dependencies}
Dependencies include softwares or framework that need to be installed for proper working of this software.

This addon could be installed on any given list of operating system.

\begin{enumerate}
	\item Mac OS X
	\item Windows
	 \begin{enumerate} 
	 	\item XP or newer on x86 32/64 bit
	 \end{enumerate}
	\item Linux
	\begin{enumerate} 
		\item Debian 
		\item Ubuntu 
		\item Kubuntu
		\item Arch Linux
		\item openSUSE
		\item Fedora
	 \end{enumerate}
	\item BSD
	\begin{enumerate}
		\item NetBSD  $\geq 6.1$
		\item FreeBSD $\geq 10 $
		\item OpenBSD
	\end{enumerate}
\end{enumerate}	 
 

The main dependencies of rebar addon is FreeCAD (version >=0.17). But If you want to build FreeCAD this software from soucre code on \emph{any OS}, you need some libraries and tools. The version
numbers in brackets specify the versions which have been used for
development. Other versions may or may not work as well.

If you're using a newer version of Ubuntu, you can install these 
libraries from aptitude. If you're using Mac, or an older Linux/BSD, there 
are build scripts that download and compile the libraries from source. 
Follow the instructions for the platform you're compiling on below. Following are
dependencies of FreeCAD software.

\begin{enumerate} 
	\item A C++ compiler supporting C++11
	\item build-essential
	\item python
	\item python-matplotlib
	\item libtool
	\item libcoin60-dev (Debian Wheezy, Wheezy-backports, Ubuntu 13.04 and before)
	\item libsoqt4-dev
	\item libxerces-c-dev
	\item libboost-dev
	\item libboost-filesystem-dev
	\item libboost-regex-dev
	\item libboost-program-options-dev
	\item python-pyside
	\item libqt4-opengl-dev
	\item qt4-dev-tools
	\item libboost-thread-dev
	\item libboost-python-dev
\end{enumerate}
