\section{Product Perspective}
   
This product is supposed to be part of an open source, under the GNU General Public license. It is a software to create the maps by using various softwares like mapnik, database, mod\_tile, openstreetmap-carto, osm2pgsql. Democratic maps is the idea given by the user's only to fullfill their needs. It had been in demand even before it consentment. It will extent this already powerfull system by allowing the user to create an OSM tile server with automation script. It will also provide a way to modify the set of parameters using config file.
   
The following are the main features that are included in Democratic maps.

\begin{enumerate}
    \item \textbf{Cross platform support:} Offers operating support for most of the known and commercial operating systems in form of binaries and also it can be compiled on other platforms.
   
    \item \textbf{Styling of Map:} Colors of the buildings, roads, primary lines, secondary lines etc have been cus-
	    tomized and then re-render the map to view the changes in the map.
   
    \item \textbf{Language Customizer:} Customize the language of the map by applying Algorithm- if Punjabi name is
	    provided then first priority goes to it followed by hindi and then English.
   
    \item \textbf{Configurable OSM Automation tile server:} It is the shell non- interactive, one time configurable script (user have to
	    change hardly two three parameters inside it) at the initial stage and then can run the script.
   
   
    \item \textbf{Event Handling:} It is used to control the movement of the map through the arrow keys of
	    keyboard.
    
    \item \textbf{3-D View of the Map:} It represents OSM Buildings with
	    multiple storyes, shadows of the building, sun, sky and many more. Most of these features
		are implemented with JOSM tool like creating 3-D tank.
   
\end{enumerate}  
